Clonal interference between aneuploidy and mutation

### 2021-05-25 ms/ms.tex
finished multiple-locus model description

\begin{equation} 
w_g= 
\begin{cases}
   1, & \text{wildtype} \\
	1-c+s_b, & \text{aneuploid wildtype} \\
	\prod_{\text{i is mutation in g}}{(1+s_i)}, & \text{euploid mutant} \\ 
	s_b+(1-c)\prod_{\text{i is mutation in g}}{(1+s_i)}, & \text{aneuploid mutant}
\end{cases}
\end{equation}

@@

Denote by $n_g$ be the number of cells of genotype $g$ in the population. At each generation, genotypes frequencies are changed by the following steps:
\begin{enumerate}
	\item Selection step: 
	\begin{equation} \label{eq:multiple-selection} 
		n_g\gets{n_g\cdot{w_g}}
	\end{equation}
	\item Random drift step:
	\begin{equation} \label{eq:multiple-rand-drift} \begin{aligned}
			f \sim Mult(N', (\frac{n_1}{N'},\frac{n_2}{N'},...)) \text{ where } N'=n_1+n_2+... 
		\end{aligned}
	\end{equation}
	\item Normalization after N change (growth or dilution):
	\begin{equation} \label{eq:multiple-pop-size} 
		n_g\gets{f_g\cdot{N}}
	\end{equation}
\end{enumerate}

>>>>

\begin{equation} \label{eq:multiple-fitness}
w_g= 
\begin{cases}
   1, & \text{wildtype} \\
	1-c+s_b, & \text{aneuploid wildtype} \\
	\prod_{\text{i is mutation in g}}{(1+s_i)}, & \text{euploid mutant} \\ 
	s_b+(1-c)\prod_{\text{i is mutation in g}}{(1+s_i)}, & \text{aneuploid mutant}
\end{cases}
\end{equation}

@@

Denote by $n_g$ be the number of cells of genotype $g$ in the population. At each generation, genotypes frequencies are changed by the following steps:
\begin{enumerate}
	\item Selection step: 
	\begin{equation} \label{eq:multiple-selection} 
		n_g\gets{n_g\cdot{w_g}}
	\end{equation}
	\item Random drift step:
	\begin{equation} \label{eq:multiple-rand-drift} \begin{aligned}
			f \sim Mult(N', (\frac{n_1}{N'},\frac{n_2}{N'},...)) \text{ where } N'=n_1+n_2+... 
		\end{aligned}
	\end{equation}
	\item Normalization after population size N change (growth or dilution):
	\begin{equation} \label{eq:multiple-pop-size} 
		n_g\gets{f_g\cdot{N}}
	\end{equation}
	\item Mutation step: \\
	For each genotype $g$, draw the number of mutant cells from a binomial distribution $Bin(n_g, \mu)$, and subtract that number from $n_g$. For each mutant cell, generate a new genotype and add one cell of this genotype to the population. The newly created genotype inherits mutations and ploidy karyotype from the parent genotype $g$, and in addition gains one more mutation, with the selected coefficient drawn from the exponential distribution $Exp(\lambda)$. The fitness of the newly created genotype is assigned according to the Formula \ref{eq:multiple-fitness}.
	\item Aneuploidy gain step: \\
	For each genotype $g$ that doesn’t already have an aneuploid chromosome, draw the number of new cells that gain aneuploidy from a binomial distribution $z \sim Bin(n_g, \alpha)$. If $z > 0$, then subtract it from $n_g$ and create a new genotype and add to the population with $z$ cells of this genotype. The genotype inherits all the mutations of genotype $g$ and in addition gains aneuploidy. The fitness is calculated appropriately by the Formula \ref{eq:multiple-fitness}.
	\item Aneuploidy loss step: \\
	It is similar to the aneuploidy step. For each genotype $g$ that has aneuploidy, draw the number of new cells that lose aneuploidy from the binomial distribution $z \sim Bin(n_g,\alpha_l)$. If $z>0$, subtract $z$ from $n_g$, then create new genotype, and add to the population $z$ cells of this genotype. The genotype inherits all the mutations of $g$ and in addition gains aneuploidy. The fitness is calculated appropriately by the Formula \ref{eq:multiple-fitness}.
\end{enumerate}

\paragraph*{Parameters inference.}
